---
title: "Reddit_Analysis"
author: "Kyra Brown"
date: "2026-06-05"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r}
library(tidyverse)
library(dplyr)
library(ggplot2)
library(readr)
library(Rtsne)
library(ggrepel)
```

1) Grouping demographics data of participants by calculating a short and long form score for each, finding the general median, then splitting participants based on that median.

```{r}
demographics <- read.csv("../Data/cleaned_data/demographics_data.csv")
demographics <- demographics %>% mutate (
  long_form_score = long_NewsArticles + long_FictionBooks + long_NonFictionBooks + long_EssaysBlogsNewsletters + long_Podcasts,
  short_form_score = social_Twitter + social_Facebook + social_TikTok + social_Reddit + social_YouTube + social_Instagram + social_Snapchat
)

median_long_form <- median(demographics$long_form_score, na.rm = TRUE) #9
median_short_form <- median(demographics$short_form_score, na.rm = TRUE) #11

demographics <- demographics %>% mutate (
  language_exposure_group = case_when(
    long_form_score < median_long_form & short_form_score < median_short_form ~ "low_long_low_short",
    long_form_score < median_long_form & short_form_score >= median_short_form ~ "low_long_high_short",
    long_form_score >= median_long_form & short_form_score < median_short_form ~ "high_long_low_short",
    long_form_score >= median_long_form & short_form_score >= median_short_form ~ "high_long_high_short",
  )
  )

demographics %>% 
  count(language_exposure_group)
```

2) Forming clusters for subreddits (entertainment, advice, academic, learning, geographic, creative, news, athletic, career, cosmetic, general, food, music, religion (NA, for any which didn't fit these categories))

```{r}
subreddit_data <- read_csv("../Data/cleaned_data/subreddit_data.csv")
subreddit_counts <- subreddit_data %>% 
  count(corrected_subreddit, sort = TRUE)
View(subreddit_counts)

top_150_subs <- subreddit_data %>% 
  count(corrected_subreddit, sort = TRUE) %>%
  head(150)

#subreddit categories manually coded, see "top_150_subs_categorized.csv."

category_map <- read_csv("top_150_subs_categorized.csv")
subreddit_data_categorized <- subreddit_data %>% left_join(category_map, by = "corrected_subreddit")
view(subreddit_data_categorized)

subreddit_data_categorized <- subreddit_data %>% left_join(category_map, by = "corrected_subreddit") %>% left_join(category_map, by = c("alt_subreddit_1" = "corrected_subreddit"), suffix = c("", "_alt")) %>% dplyr::mutate(category = coalesce(category, category_alt)) %>% dplyr::select(-category_alt)
subreddit_data_categorized %>% count(category, sort = TRUE)
```

3) Fluency and interest correlations calculated and range box plots (interest and fluency spread) formed

```{r}
fluency_wide <- read.csv("../Data/cleaned_data/fluency_interest_estimate.csv")%>%
  select(-rt)%>%
  pivot_wider(names_from = typeoftrial, values_from = response)
View(fluency_wide)

#Box plot of interest spread across domains
ggplot(fluency_wide, aes(x = domain, y = VFT_category_interest)) + geom_boxplot() + labs(title = "Interest Spread by Domain")
ggsave("interest_spread_by_domain_plot.png", width = 8, height = 6)

#Box plot of fluency spread across domains
ggplot(fluency_wide, aes(x = domain, y = VFT_estimate)) + geom_boxplot() + labs(title = "Fluency Spead by Domain")
ggsave("fluency_spread_by_domain_plot.png", width = 8, height = 6)

#Summary of correlation between fluency and interest per domain
fluency_wide %>% group_by(domain) %>% summarize(correlation = cor(VFT_category_interest, VFT_estimate, use = "complete.obs"))

#Plot of correlation, annotated ^
correlation_labels <- fluency_wide %>%
  group_by(domain) %>%
  summarize(correlation = round(cor(VFT_category_interest, VFT_estimate, use = "complete.obs"), 2), x = 85, y = max(VFT_estimate, na.rm = TRUE) * 0.9)
correlation_labels$y <- c(55, 50, 45, 40, 35)

ggplot(fluency_wide, aes(x = VFT_category_interest, y = VFT_estimate, color = domain)) + geom_point(alpha = 0.4) + geom_smooth(method = "lm", se = FALSE) + geom_text(
  data = correlation_labels, aes(x = x, y = y, label = paste0("r" = correlation), color = domain), show.legend = FALSE, size = 3.5) +
  labs(title = "Fluency vs Interest Correlation by Domain", x = "Category Interest", y = "Fluency Estimate", color = "Domain") + theme_minimal()
ggsave("fluency_interest_by_domain_correlation_plot.png", width = 8, height = 6)
```
4) t-SNE of interest data
```{r}
emb <- read_csv("../Analysis/forager/data/lexical_data/interests/USE_embeddings.csv")

X <- t(as.matrix(emb))
labels <- colnames(emb)
dim(X)
head(labels)

dim(emb)
dim(tsne_out$Y)
ncol(emb)
nrow(emb)

set.seed(123)
tsne_out <- Rtsne(X, perplexity = 15, check_duplicates = FALSE, pca = TRUE)
tsne_df <- data.frame(interest = labels, x = tsne_out$Y[,1], y = tsne_out$Y[,2])

ggplot(tsne_df, aes(x, y, label = interest)) + geom_point(size = 2) + geom_text_repel(size = 3) + theme_minimal()

```

5) Preparation for Forager (semantic embeddings, cues, frequencies)
```{r}
#Unique vocab lists

#Authors
unique_author_enteries <- read.csv("../Data/cleaned_data/fluency_data.csv") %>%
  filter(domain == "authors") %>% distinct(corrected_response)
View(unique_author_enteries)
write.csv(unique_author_enteries, "Analysis/forager/data/lexical_data/authors/vocab.csv", row.names = FALSE)

#Musicians
unique_musician_enteries <- read.csv("../Data/cleaned_data/fluency_data.csv") %>%
  filter(domain == "musicians") %>% distinct(corrected_response)
View(unique_musician_enteries)
write.csv(unique_musician_enteries, "Analysis/forager/data/lexical_data/musicians/vocab.csv", row.names = FALSE)

#Sportspersons
unique_sportspersons_enteries <- read.csv("../Data/cleaned_data/fluency_data.csv") %>%
  filter(domain == "sportspersons") %>% distinct(corrected_response)
View(unique_sportspersons_enteries)
write.csv(unique_sportspersons_enteries, "Analysis/forager/data/lexical_data/sportspersons/vocab.csv", row.names = FALSE)

#College Majors
unique_college_majors_enteries <- read.csv("../Data/cleaned_data/fluency_data.csv") %>%
  filter(domain == "college_majors") %>% distinct(corrected_response)
View(unique_college_majors_enteries)
write.csv(unique_college_majors_enteries, "Analysis/forager/data/lexical_data/college majors/vocab.csv", row.names = FALSE)

path <- "Analysis/forager/data/lexical_data/college majors/vocab.csv"
read.csv(path) %>% rename(vocab = corrected_response) %>% write.csv(path, row.names = FALSE)

#Interests
unique_interest_enteries <- read.csv("../Data/cleaned_data/interests_data.csv") %>%
  distinct(corrected_interest) %>% rename(vocab = corrected_interest)
View(unique_interest_enteries)
write.csv(unique_interest_enteries, "Analysis/forager/data/lexical_data/interests/vocab.csv", row.names = FALSE)

```

5) Preparation for Forager (phonological matricies)
```{r}
#Changing column name
base_path <- "../Analysis/forager/Data/lexical_data"

domains <- c("authors", "musicians", "sportspersons", "college majors")

for(domain in domains) {
  path <- file.path(base_path, domain, "vocab.csv")
  df <- read.csv(path, stringsAsFactors = FALSE)
  
  if ("vocab" %in% names(df)) {
    df <- df %>% rename(word = vocab)
  }
  
  #Finding weird entries/duplicates
  cat("\n---", domain, "---\n")
  
  duplicates <- df$word[duplicated(df$word)]
  if (length(duplicates) > 0) cat("Duplicates:", paste(duplicates, collapse = ", "), "\n")
  
  weird_chars <- df$word[grepl("[^a-zA-Z0-9 ., '-]|\\(|\\)", df$word)]
  if (length(weird_chars) > 0) cat("Weird Characters:", paste(weird_chars, collapse = ", "), "\n")
  
  #Cleaning data
  df$word <- stri_trans_general(df$word, "Latin-ASCII")
  df$word <- gsub("\\+", " and ", df$word)
  df$word <- gsub("&", " and ", df$word)
  df$word <- gsub("\\s*\\([^)]*\\)", "", df$word)
  df$word <- gsub("[^a-zA-Z0-9 .,\\'-]", "", df$word)
  df$word <- gsub("\\s+", " ", df$word)
  df$word <- trimws(df$word)

  write.csv(df, path, row.names = FALSE)

  cat("Cleaned:", domain, "\n") 
  
}
```

Extra tests (1): Is there a connection between the variety of subreddit categories a person engaged with and their fluency?

```{r}
subreddit_variety_data <- subreddit_data_categorized %>%
  group_by(Subject) %>%
  summarize(unique_categories = n_distinct(category, na.rm = TRUE)) %>%
  left_join(fluency_wide, by = c("Subject" = "subject"))

ggplot(subreddit_variety_data, aes(x = unique_categories, y = VFT_estimate)) + geom_point() + geom_smooth(method = "lm") + labs(title = "Category Variety vs Fluency")

cor(subreddit_variety_data$unique_categories, subreddit_variety_data$VFT_estimate, use = "complete.obs")

```

Extra tests (2): Are there different fluency scores based language exposure group?

```{r}
exposure_data <- demographics %>%
  left_join(fluency_wide, by = "subject")

ggplot(exposure_data, aes(x = language_exposure_group, y = VFT_estimate)) + geom_boxplot() + theme(axis.text.x = element_text(angle = 45, hjust = 1)) + labs(title = "Fluency by Language Exposure")

#ANOVA testing if fluency differs across exposure, at least one group has a different mean fluency than the others
summary(aov(VFT_estimate ~ language_exposure_group, data = exposure_data))

#Tukey's test, reveling significant difference between low long, high short and other groups in fluency production
TukeyHSD(aov(VFT_estimate ~ language_exposure_group, data = exposure_data))
```
