---
title: "Reddit_Analysis"
author: "Kyra Brown"
date: "2026-06-05"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r}
library(tidyverse)
library(dplyr)
library(ggplot2)
library(readr)
library(Rtsne)
library(ggrepel)
```

First, grouping demographics data of participants by calculating a short and long form score for each, finding the general median, then splitting participants based on that median.

```{r}
demographics <- read.csv("ADD PATH TO YOUR demographics.csv")
demographics <- demographics %>% mutate (
  long_form_score = long_NewsArticles + long_FictionBooks + long_NonFictionBooks + long_EssaysBlogsNewsletters + long_Podcasts,
  short_form_score = social_Twitter + social_Facebook + social_TikTok + social_Reddit + social_YouTube + social_Instagram + social_Snapchat
)

median_long_form <- median(demographics$long_form_score, na.rm = TRUE) #9
median_short_form <- median(demographics$short_form_score, na.rm = TRUE) #11

demographics <- demographics %>% mutate (
  language_exposure_group = case_when(
    long_form_score < median_long_form & short_form_score < median_short_form ~ "low_long_low_short",
    long_form_score < median_long_form & short_form_score >= median_short_form ~ "low_long_high_short",
    long_form_score >= median_long_form & short_form_score < median_short_form ~ "high_long_low_short",
    long_form_score >= median_long_form & short_form_score >= median_short_form ~ "high_long_high_short",
  )
  )

demographics %>% 
  count(language_exposure_group)
```

Next, forming clusters for subreddits (entertainment, advice, academic, learning, geographic, creative, news, athletic, career, cosmetic, general, food, music, religion (NA, for any which didn't fit these categories))

```{r}
subreddit_data <- read_csv("~/Library/CloudStorage/OneDrive-BowdoinCollege/Desktop/fluency-individual-variance/Data/subreddit_data (1).csv")
subreddit_counts <- subreddit_data %>% 
  count(corrected_subreddit, sort = TRUE)
View(subreddit_counts)

top_150_subs <- subreddit_data %>% 
  count(corrected_subreddit, sort = TRUE) %>%
  head(150)

#subreddit categories manually coded, see "top_150_subs_categorized.csv."

category_map <- read_csv("top_150_subs_categorized.csv")
subreddit_data_categorized <- subreddit_data %>% left_join(category_map, by = "corrected_subreddit")
view(subreddit_data_categorized)

subreddit_data_categorized <- subreddit_data %>% left_join(category_map, by = "corrected_subreddit") %>% left_join(category_map, by = c("alt_subreddit_1" = "corrected_subreddit"), suffix = c("", "_alt")) %>% dplyr::mutate(category = coalesce(category, category_alt)) %>% dplyr::select(-category_alt)
subreddit_data_categorized %>% count(category, sort = TRUE)
```

Finally, fluency and interest correlations calculated and range box plots (interest and fluency spread) formed

```{r}
fluency_wide <- read.csv("~/Library/CloudStorage/OneDrive-BowdoinCollege/Desktop/fluency-individual-variance/Data/fluency_interest_estimate.csv")%>%
  select(-rt)%>%
  pivot_wider(names_from = typeoftrial, values_from = response)
View(fluency_wide)

ggplot(fluency_wide, aes(x = domain, y = VFT_category_interest)) + geom_boxplot() + labs(title = "Interest Spread by Domain")
ggsave("interest_spread_by_domain_plot.png", width = 8, height = 6)

ggplot(fluency_wide, aes(x = domain, y = VFT_estimate)) + geom_boxplot() + labs(title = "Fluency Spead by Domain")
ggsave("fluency_spread_by_domain_plot.png", width = 8, height = 6)

fluency_wide %>% group_by(domain) %>% summarize(correlation = cor(VFT_category_interest, VFT_estimate, use = "complete.obs"))
```
t-SNE of interest data
```{r}
emb <- read_csv("~/Library/CloudStorage/OneDrive-BowdoinCollege/Documents/GitHub/fluency-individual-variance/Analysis/forager/data/lexical_data/interests/USE_embeddings.csv")

X <- t(as.matrix(emb))
labels <- colnames(emb)
dim(X)
head(labels)

dim(emb)
dim(tsne_out$Y)
ncol(emb)
nrow(emb)

set.seed(123)
tsne_out <- Rtsne(X, perplexity = 15, check_duplicates = FALSE, pca = TRUE)
tsne_df <- data.frame(interest = labels, x = tsne_out$Y[,1], y = tsne_out$Y[,2])

ggplot(tsne_df, aes(x, y, label = interest)) + geom_point(size = 2) + geom_text_repel(size = 3) + theme_minimal()

```


Extra tests (1): Is there a connection between the variety of subreddit categories a person engaged with and their fluency?

```{r}
subreddit_variety_data <- subreddit_data_categorized %>%
  group_by(Subject) %>%
  summarize(unique_categories = n_distinct(category, na.rm = TRUE)) %>%
  left_join(fluency_wide, by = c("Subject" = "subject"))

ggplot(subreddit_variety_data, aes(x = unique_categories, y = VFT_estimate)) + geom_point() + geom_smooth(method = "lm") + labs(title = "Category Variety vs Fluency")

cor(subreddit_variety_data$unique_categories, subreddit_variety_data$VFT_estimate, use = "complete.obs")
```

Extra tests (2): Are there different fluency scores based language exposure group?

```{r}
exposure_data <- demographics %>%
  left_join(fluency_wide, by = c("run_id" = "subject"))

ggplot(exposure_data, aes(x = language_exposure_group, y = VFT_estimate)) + geom_boxplot() + theme(axis.text.x = element_text(angle = 45, hjust = 1)) + labs(title = "Fluency by Language Exposure")

summary(aov(VFT_estimate ~ language_exposure_group, data = exposure_data))
```
