---
title: "Reddit_Analysis"
author: "Kyra Brown"
date: "2026-06-05"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r}
library(tidyverse)
library(dplyr)
library(ggplot2)
library(readr)
library(Rtsne)
library(ggrepel)
library(tidyr)
library(stringr)
library(lme4)
library(lmerTest)
library(purrr)
library(broom.mixed)
library(patchwork)
```

1) Grouping demographics data of participants into high short/long, low short/long, high short low long, and low short high long and comparing across lexical data.

```{r}
#Loading demographics data
demographics <- read.csv("../Data/cleaned_data/demographics_data.csv")

#Calculates scores for long form (articles, books, newsletters, podcasts, etc) and short form (social media) language exposure for each participant
demographics <- demographics %>% mutate (
  long_form_score = long_NewsArticles + long_FictionBooks + long_NonFictionBooks + long_EssaysBlogsNewsletters + long_Podcasts,
  short_form_score = social_Twitter + social_Facebook + social_TikTok + social_Reddit + social_YouTube + social_Instagram + social_Snapchat
)

#Calculates median scores used to split participants into groups
median_long_form <- median(demographics$long_form_score, na.rm = TRUE) #9
median_short_form <- median(demographics$short_form_score, na.rm = TRUE) #11

#Assigns participants to one of four language exposure groups based on the median in each type of content
demographics <- demographics %>% mutate (
  language_exposure_group = case_when(
    long_form_score < median_long_form & short_form_score < median_short_form ~ "low_long_low_short",
    long_form_score < median_long_form & short_form_score >= median_short_form ~ "low_long_high_short",
    long_form_score >= median_long_form & short_form_score < median_short_form ~ "high_long_low_short",
    long_form_score >= median_long_form & short_form_score >= median_short_form ~ "high_long_high_short",
  )
  )

#Gets count of how many participants fall into every group
demographics %>% 
  count(language_exposure_group)

#Loads in forager lexical results for each domain and combines them into one dataset
all_lexical_results <- bind_rows(read_csv("forager/output/animals_forager_results/lexical_results.csv") %>%
                                   mutate(domain = "animals", Subject = as.character(Subject)),
                                 read_csv("forager/output/authors_forager_results/lexical_results.csv") %>%
                                   mutate(domain = "authors", Subject = as.character(Subject)),
                                 read_csv("forager/output/college_majors_forager_results/lexical_results.csv") %>%
                                   mutate(domain = "college_majors", Subject = as.character(Subject)),
                                 read_csv("forager/output/musicians_forager_results/lexical_results.csv") %>%
                                   mutate(domain = "musicians", Subject = as.character(Subject)),
                                 read_csv("forager/output/sportspersons_forager_results/lexical_results.csv") %>%
                                   mutate(domain = "sportspersons", Subject = as.character(Subject)),
                                 )

#Combines lexical results with demographics results, adding langiage exposure data   
lexical_language_exposure_groups <- all_lexical_results %>%
  left_join(demographics %>% select(subject, language_exposure_group), by = c("Subject" = "subject"))

#Removes any participants who weren't matched properly to a language exposure group
lexical_language_exposure_groups <- lexical_language_exposure_groups %>% filter(!is.na(language_exposure_group))

#Calculates the semantic/phonological similarity and word frequency for each domain and language exposure group
participant_summary <- lexical_language_exposure_groups %>%
  group_by(Subject, domain, language_exposure_group) %>%
  summarise(mean_semantic = mean(Semantic_Similarity, na.rm = TRUE),
            mean_phonological = mean(Phonological_Similarity, na.rm = TRUE),
            mean_frequency = mean(Frequency_Value, na.rm = TRUE),
            .groups = "drop")
lexical_summary <- participant_summary %>% 
  group_by(domain, language_exposure_group) %>%
  summarise(mean_semantic = mean(mean_semantic, na.rm = TRUE),
            mean_phonological = mean(mean_phonological, na.rm = TRUE),
            mean_frequency = mean(mean_frequency, na.rm = TRUE),
            .groups = "drop")

lexical_summary_long_form <- lexical_summary %>%
  pivot_longer(
    cols = c(mean_semantic, mean_phonological, mean_frequency),
    names_to = "cue",
    values_to = "value"
  )

ggplot(lexical_summary_long_form, aes(x = language_exposure_group, y = value, fill = language_exposure_group)) +
  geom_col() + facet_grid(cue ~ domain, scales = "free_y", labeller = labeller(
    cue = c(
      mean_semantic = "Sem. Similarity",
      mean_phonological = "Phon. Similarity",
      mean_frequency = "Frequency"
    )
  )) +
  labs(
    title = "Lexical Cues Across Language Exposure Groups", x = NULL, y = "Mean Value") +
  theme_minimal() + theme(axis.text.x = element_text(angle = 45, hjust = 1), legend.title = element_blank()
  )
  
```

2) Forming clusters for subreddits (entertainment, advice, academic, learning, geographic, creative, news, athletic, career, cosmetic, general, food, music, religion (NA, for any which didn't fit these categories))

```{r}
subreddit_data <- read_csv("../Data/cleaned_data/subreddit_data.csv")
subreddit_counts <- subreddit_data %>% 
  count(corrected_subreddit, sort = TRUE)
#View(subreddit_counts)

top_150_subs <- subreddit_data %>% 
  count(corrected_subreddit, sort = TRUE) %>%
  head(150)

#subreddit categories manually coded, see "top_150_subs_categorized.csv."

category_map <- read_csv("top_150_subs_categorized.csv")
subreddit_data_categorized <- subreddit_data %>% left_join(category_map, by = "corrected_subreddit")
#view(subreddit_data_categorized)

subreddit_data_categorized <- subreddit_data %>% left_join(category_map, by = "corrected_subreddit") %>% left_join(category_map, by = c("alt_subreddit_1" = "corrected_subreddit"), suffix = c("", "_alt")) %>% dplyr::mutate(category = coalesce(category, category_alt)) %>% dplyr::select(-category_alt)
subreddit_data_categorized %>% count(category, sort = TRUE)
```

Categorizing Subreddit preferences by participant's first input

```{r}
subreddit_data <- read_csv("../Data/cleaned_data/subreddit_data.csv")
subreddit_counts <- subreddit_data %>% 
  count(corrected_subreddit, sort = TRUE)
#View(subreddit_counts)

top_150_subs <- subreddit_data %>% 
  count(corrected_subreddit, sort = TRUE) %>%
  head(150)

category_map <- read_csv("../Analysis/top_150_subs_categorized.csv")

manually_added_categories <- tribble(
  ~corrected_subreddit, ~category,
  "r/BPD", "advice",
  "r/Baking", "food",
  "r/Barca", "athletic",
  "r/BostonBruins", "athletic",
  "r/Breath_of_the_Wild", "entertainment",
  "r/Biohackers", "learning",
  "r/BostonBruins", "athletic",
  "r/Buddhism", "religion",
  "r/CFB", "athletic",
  "r/Catholicism", "religion",
  "r/ChatGPT", "learning",
  "r/Costco", "food",
  "r/CozyPlaces", "entertainment",
  "r/CrumblCookies", "food",
  "r/Dreams", "advice",
  "r/EDC", "advice",
  "r/EDH", "entertainment",
  "r/EngagementRings", "creative",
  "r/FigureSkating", "athletic",
  "r/FinancialCareers", "academic and career",
  "r/Forex", "academic and career",
  "r/FundieSnarkUncensored", "religion",
  "r/GaySoundsShitposts", "entertainment",
  "r/GaylorSwift", "entertainment",
  "r/Hair", "creative",
  "r/Handwriting", "creative",
  "r/HomeworkHelp", "academic and career",
  "r/HonkaiStarRail", "entertainment",
  "r/IdiotsInCars", "entertainment",
  "r/Indianapolis", "geographic",
  "r/Jujutsufolk", "entertainment",
  "r/MCFC", "athletic",
  "r/Millennials", "advice",
  "r/Mommit", "advice",
  "r/MurderedByWords", "entertainment",
  "r/NoSleep", "entertainment",
  "r/NonCredibleDefense", "geographic", 
  "r/Omaha", "geographic",
  "r/OnePiece", "entertainment",
  "r/Reverse1999", "entertainment",
  "r/RoastMe", "advice", 
  "r/StockMarket", "learning",
  "r/UXDesign", "academic and career",
  "r/math", "academic and career",
  "r/clinicalresearch", "academic and career",
  "r/celestegame", "entertainment",
  "r/surfing", "athletic",
  "r/TraderJoes", "food",
  "r/asexuality", "advice",
  "r/apples", "food",
  "r/ftm", "advice",
  "r/uswnt", "athletic",
  "r/sentinelsmultiverse", "entertainment",
  "r/deloitte", "academic and career",
  "r/peloton", "athletic",
  "r/philosophy", "learning",
  "r/vegan", "food",
  "r/rance", "geographic",
  "r/simpleliving", "learning",
  "r/tea", "food",
  "r/whatisthisbird", "learning",
  "r/vexillology", "learning",	
  "r/trees", "food",
  "r/foodiesnark", "food"			
 )

category_map_complete <- bind_rows(category_map, manually_added_categories)
  

subreddit_data_categorized <- subreddit_data %>%
  left_join(category_map_complete, by = "corrected_subreddit") %>%
  left_join(category_map_complete, by = c("alt_subreddit_1" = "corrected_subreddit"), suffix = c("", "_alt1")) %>%
  left_join(category_map_complete, by = c("alt_subreddit_2" = "corrected_subreddit"), suffix = c("", "_alt2")) %>%
  mutate(category = coalesce(category, category_alt1, category_alt2)) %>%
  select(-category_alt1, -category_alt2)

#view(subreddit_data_categorized)
subreddit_data_categorized %>% count(category, sort = TRUE)

subreddit_data_categorized <- subreddit_data_categorized %>%
  mutate(category = replace_na(category, "other"))

primary_buckets <- subreddit_data_categorized %>%
  filter(tag == 1) %>%
  transmute(Subject, primary_subreddit = corrected_subreddit, primary_bucket = category)

df_analysis <- subreddit_data_categorized %>%
  left_join(primary_buckets, by = "Subject") %>%
  mutate(matches_primary = (category == primary_bucket))

other_subreddit_alignment_check <- df_analysis %>%
  group_by(Subject, primary_subreddit, primary_bucket) %>%
  summarise(
    total_subreddits = n(),
    matching_category = sum(matches_primary, na.rm = TRUE),
    unknown_category = sum(is.na(category)),
    percentage_match = round(100 * matching_category / total_subreddits, 1),
    mismatched_subreddits = paste(corrected_subreddit[!matches_primary & !is.na(category)], collapse = ", "), .groups = "drop"
  ) %>%
  arrange(desc(percentage_match))

print(other_subreddit_alignment_check, n = Inf)

category_distribution <- df_analysis %>%
  count(category, sort = TRUE) %>%
  mutate(pct = round(100 * n / sum(n), 1))

print(category_distribution)

subreddit_data_categorized %>%
  filter(is.na(category))%>%
  count(corrected_subreddit, sort = TRUE)

other_subreddit_alignment_check %>%
  filter(primary_bucket == "other") %>%
  select(Subject, primary_subreddit)

primary_bucket_summary <- primary_buckets %>%
  count(primary_bucket, sort = TRUE) %>%
  mutate(pct = round(100 * n / sum(n), 1))
print(primary_bucket_summary)

participant_consistency_summary <- other_subreddit_alignment_check %>%
  group_by(primary_bucket) %>%
  summarise(
    n_participants = n(),
    average_pct_match = round(mean(percentage_match, na.rm = TRUE), 1),
    median_pct_match = round(median(percentage_match, na.rm = TRUE), 1)) %>%
  arrange(desc(n_participants))
print(participant_consistency_summary)

other_subreddit_alignment_check %>%
  filter(primary_bucket == "religion")

primary_buckets %>%
  filter(primary_bucket == "religion")

  
```

Plots of subreddits listed, first subreddit stats, and subreddit category consistency

```{r}
#distribution of subreddits listed per participant
subreddit_count_per_participant <- subreddit_data_categorized %>%
  group_by(Subject) %>%
  summarise(n_subreddits = n())

subreddit_count_plot <- ggplot(subreddit_count_per_participant, aes(x = n_subreddits)) + 
  geom_bar(fill = "steelblue") +
  scale_x_continuous(breaks = seq(0, 30, 5)) +
  labs(
    title = "Distribution of Subreddit Count Per Participant",
    x = "Number of Subreddits Listed",
    y = "Participant #") + theme_minimal()


#distribution of primary buckets people's first subreddit input fell into
primary_bucket_plot <- ggplot(primary_bucket_summary, aes(x = reorder(primary_bucket, pct), y = pct)) +
  geom_col(fill = "steelblue") +
  coord_flip() +
  scale_y_continuous(breaks = seq(0, 30, 5)) +
  labs(
    title = "First Subreddit Category Distribution",
    x = "Category",
    y = "Percentage of Participants (%)"
  ) + theme_minimal()

#Participant consistency based on primary bucket
consistency_plot <- ggplot(participant_consistency_summary, aes(x = n_participants, y = average_pct_match, size = n_participants, label = primary_bucket)) +
  geom_point(alpha = 0.6, color = "steelblue") +
  geom_text(vjust = -1, size = 3) +
  scale_size_continuous(range = c(3, 12)) + 
  scale_x_continuous(breaks = seq(0, 30, 5)) +
  scale_y_continuous(breaks = seq(0, 60, 5)) +
  labs(
    title = "Category Consistency vs. Popularity",
    x = "Number of Participants",
    y = "Avg % Subreddit Primary Category Match",
    size = "N Participants",
  ) +
  theme_minimal() + theme(legend.position = "none")

(subreddit_count_plot | primary_bucket_plot) / consistency_plot

```

 subreddits named over time (in 30 second intervals)
 
```{r}
reddit_raw_data <- read_csv("../Data/raw_data/reddit_data.csv")

subreddit_reaction_time <- reddit_raw_data %>%
  filter(task == "VFT", domain == "subreddits") %>%
  select(subject, response_times) %>%
  
mutate(response_times = str_remove_all(response_times, "\\[|\\]")) %>%
  separate_rows(response_times, sep = ",") %>%
  mutate(response_times = as.numeric(str_trim(response_times))) %>%
  group_by(subject) %>%
  mutate(
    subreddit_number = row_number(),
    cumulative_rt_s = cumsum(response_times) / 1000
  ) %>%
  ungroup()

max_time <- ceiling(max(subreddit_reaction_time$cumulative_rt_s, na.rm = TRUE))

subjects <- unique(subreddit_reaction_time$subject)

number_of_subjects <- length(subjects)

percentage_cumulative_curve <- tibble(second = 1:max_time) %>%
  mutate(
    avg_subreddits = sapply(second, function(s) {
      mean(sapply(subjects, function(subj) {
        sum(subreddit_reaction_time$cumulative_rt_s[subreddit_reaction_time$subject == subj] <= s, na.rm = TRUE)
      }))
    }),
    percent_named_one_subreddit = sapply(second, function(s) {
      100 * mean(sapply(subjects, function(subj) {
        any(subreddit_reaction_time$cumulative_rt_s[subreddit_reaction_time$subject == subj] <= s, na.rm = TRUE)
      }))
    })
  )

print(percentage_cumulative_curve, n = 90)

average_items_plot <- ggplot(percentage_cumulative_curve, aes(x = second, y = avg_subreddits)) +
  geom_col(color = "steelblue") + 
  scale_x_continuous(breaks = seq(0, max_time, 30)) +
  scale_y_continuous(breaks = seq(0, ceiling(max(percentage_cumulative_curve$avg_subreddits)), 1)) +
  labs(
    title = "Cumulative Average Subreddits Named Over Time",
    x = "Cumulative Time (seconds)",
    y = "Average Number of Subreddits Named"
  ) + theme_minimal() +
  theme(
  plot.title = element_text(size = 11)
)

percentage_plot <- ggplot(percentage_cumulative_curve, aes(x = second, y = percent_named_one_subreddit)) +
  geom_line(color = "steelblue", linewidth = 1) + 
  coord_cartesian(xlim = c(0,30)) +
  scale_x_continuous(breaks = seq(0, 30, 5)) +
  scale_y_continuous(breaks = seq(0,100, 10), limits = c(0, 100)) +
  labs(
    title = "Participants Naming >= 1 Subreddit",
    x = "Cumulative Time (seconds)",
    y = "% of Participants"
  ) + theme_minimal() +
  theme(
  plot.title = element_text(size = 11)
)

average_items_plot | percentage_plot

```
Domain inputs named over time
```{r}
all_domain_curves <- tibble()
all_first_item_rt <- tibble()

fluency_domains <- c("animals", "authors", "college_majors", "musicians", "sportspersons")

for (dom in fluency_domains) {
  fluency_rt <- reddit_raw_data %>%
    filter(task == "VFT", domain == dom) %>%
    select(subject, response_times) %>%
    mutate(response_times = str_remove_all(response_times, "\\[|\\]")) %>%
    separate_rows(response_times, sep = ",") %>%
    mutate(response_times = as.numeric(str_trim(response_times))) %>%
    group_by(subject) %>%
    mutate(item_number = row_number(), cumulative_rt_s = cumsum(response_times) / 1000) %>%
    ungroup()
  
  max_time <- ceiling(max(fluency_rt$cumulative_rt_s, na.rm = TRUE))
  subjects <- unique(fluency_rt$subject)
  
  fluency_curve <- tibble(second = 1:max_time) %>%
    mutate(
      avg_items = sapply(second, function(s) { 
      mean(sapply(subjects, function(subj) { 
        sum(fluency_rt$cumulative_rt_s[fluency_rt$subject == subj] <= s,
            na.rm = TRUE) })) }), 
      percent_named_one = sapply(second, function(s) { 
        100 * mean(sapply(subjects, function(subj) { 
          any(
            fluency_rt$cumulative_rt_s[fluency_rt$subject == subj] <= s, 
              na.rm = TRUE
              ) 
          })) 
        })
      )
    
  fluency_curve <- fluency_curve %>%
    mutate(domain = dom)
   
  first_item_rt <- fluency_rt %>%
    filter(item_number == 1) %>%
    mutate(first_rt_s = cumulative_rt_s, domain = dom)
  
  all_domain_curves <- bind_rows(all_domain_curves, fluency_curve)
  all_first_item_rt <- bind_rows(all_first_item_rt, first_item_rt)
}
  
  first_item_dist <- ggplot(all_first_item_rt, aes(first_rt_s)) +
    geom_histogram(fill = "steelblue", bins = 20) + 
    facet_wrap(~domain) +
    theme_minimal()  
  
  
  avg_items_named_over_time_plot <- ggplot(all_domain_curves, aes(x = second, y = avg_items)) +
    geom_col(fill = "steelblue") + 
    facet_wrap(~domain) +
    theme_minimal()  
  
  
  percentage_named_over_time_plot <- ggplot(all_domain_curves, aes(x = second, y = percent_named_one)) +
    geom_line(color = "steelblue") + 
    facet_wrap(~domain) +
    theme_minimal()  

combined_rt_plot <- avg_items_named_over_time_plot | percentage_named_over_time_plot

combined_rt_plot
```

Checking for outlier
```{r}
participant_summary <- subreddit_reaction_time %>%
  group_by(subject) %>%
  summarise(
    first_rt = first(cumulative_rt_s),
    n_responses = n(),
    mean_rt = mean(response_times, na.rm = TRUE) / 1000,
    median_rt = median(response_times, na.rm = TRUE) / 1000
  )

ggplot(participant_summary, aes(x = "", y = first_rt)) +
  geom_boxplot()

ggplot(participant_summary, aes(first_rt)) +
  geom_histogram(bins = 20)

ggplot(subreddit_reaction_time,
       aes(cumulative_rt_s, subreddit_number, group = subject)) +
  geom_line(alpha = 0.2) +
  theme_minimal()

participant_summary %>%
  mutate(
    z_first = scale(first_rt),
    z_mean = scale(mean_rt),
    z_n = scale(n_responses)
  ) %>%
  arrange(desc(abs(z_first)))

participant_summary


reddit_raw_data %>%
  filter(subject %in% c("ESNMRF10", "XV9JV4CP", "BWQ1ZSYD"))

highlight <- c("ESNMRF10", "XV9JV4CP", "BWQ1ZSYD")

ggplot(
  subreddit_reaction_time,
  aes(cumulative_rt_s, subreddit_number,
      group = subject,
      colour = subject %in% highlight)
) +
  geom_line(alpha = 0.7) +
  scale_colour_manual(values = c("grey80", "red")) +
  theme_minimal()


```
deviant domain participant

```{r}
fluency_domains <- c("animals", "authors", "college_majors",
                     "musicians", "sportspersons")

all_participant_summary <- tibble()

for (dom in fluency_domains) {

  fluency_rt <- reddit_raw_data %>%
    filter(task == "VFT", domain == dom) %>%
    select(subject, response_times) %>%
    mutate(response_times = str_remove_all(response_times, "\\[|\\]")) %>%
    separate_rows(response_times, sep = ",") %>%
    mutate(response_times = as.numeric(str_trim(response_times))) %>%
    group_by(subject) %>%
    mutate(
      item_number = row_number(),
      cumulative_rt_s = cumsum(response_times)/1000
    ) %>%
    ungroup()

  participant_summary <- fluency_rt %>%
    group_by(subject) %>%
    summarise(
      first_rt = first(cumulative_rt_s),
      n_responses = n(),
      mean_rt = mean(response_times, na.rm = TRUE)/1000,
      median_rt = median(response_times, na.rm = TRUE)/1000
    ) %>%
    mutate(domain = dom)

  all_participant_summary <- bind_rows(all_participant_summary,
                                       participant_summary)
}

domain_outliers <- all_participant_summary %>%
  group_by(domain) %>%
  mutate(
    z_first = as.numeric(scale(first_rt)),
    z_mean = as.numeric(scale(mean_rt)),
    z_n = as.numeric(scale(n_responses))
  ) %>%
  ungroup()

domain_outliers %>%
  filter(abs(z_first) > 3) %>%
  arrange(domain, desc(z_first))

domain_outliers %>%
  filter(z_n < -3)

domain_outliers %>%
  filter(abs(z_first) > 3 | abs(z_mean) > 3 | abs(z_n) > 3) %>%
  count(subject, sort = TRUE)

ggplot(all_participant_summary,
       aes(x = "", y = first_rt)) +
  geom_boxplot() +
  facet_wrap(~domain) +
  theme_minimal()

ggplot(all_participant_summary,
       aes(first_rt)) +
  geom_histogram(bins = 20) +
  facet_wrap(~domain)

domain_outliers %>%
  group_by(subject) %>%
  summarise(
    max_abs_z = max(abs(z_first)),
    mean_abs_z = mean(abs(z_first)),
    n_domains = n(),
    n_outlier_domains = sum(abs(z_first) > 3)
  ) %>%
  arrange(desc(max_abs_z))

domain_outliers %>%
  group_by(subject) %>%
  summarise(
    mean_items = mean(n_responses),
    total_domains = n(),
    slow_domains = sum(z_first > 3),
    low_output_domains = sum(z_n < -3)
  ) %>%
  arrange(desc(slow_domains))

overall_output <- all_participant_summary %>%
  group_by(subject) %>%
  summarise(
    total_items = sum(n_responses),
    mean_items = mean(n_responses)
  ) %>%
  arrange(total_items)

overall_output
summary(overall_output$total_items)
ggplot(overall_output, aes(total_items)) +
  geom_histogram(bins = 20) +
  theme_minimal()
```


3) Fluency and interest correlations calculated and range box plots (interest and fluency spread) formed

```{r}
fluency_wide <- read.csv("../Data/cleaned_data/fluency_interest_estimate.csv")%>%
  select(-rt)%>%
  pivot_wider(names_from = typeoftrial, values_from = response)
#View(fluency_wide)

#Box plot of interest spread across domains
ggplot(fluency_wide, aes(x = domain, y = VFT_category_interest)) + geom_boxplot() + labs(title = "Interest Spread by Domain")
ggsave("interest_spread_by_domain_plot.png", width = 8, height = 6)

#Box plot of fluency spread across domains
ggplot(fluency_wide, aes(x = domain, y = VFT_estimate)) + geom_boxplot() + labs(title = "Fluency Spead by Domain")
ggsave("fluency_spread_by_domain_plot.png", width = 8, height = 6)

#Summary of correlation between fluency and interest per domain
fluency_wide %>% group_by(domain) %>% summarize(correlation = cor(VFT_category_interest, VFT_estimate, use = "complete.obs"))

#Plot of correlation, annotated ^
correlation_labels <- fluency_wide %>%
  group_by(domain) %>%
  summarize(correlation = round(cor(VFT_category_interest, VFT_estimate, use = "complete.obs"), 2), x = 85, y = max(VFT_estimate, na.rm = TRUE) * 0.9)
correlation_labels$y <- c(55, 50, 45, 40, 35)

ggplot(fluency_wide, aes(x = VFT_category_interest, y = VFT_estimate, color = domain)) + geom_point(alpha = 0.4) + geom_smooth(method = "lm", se = FALSE) + geom_text(
  data = correlation_labels, aes(x = x, y = y, label = paste0("r" = correlation), color = domain), show.legend = FALSE, size = 3.5) +
  labs(title = "Fluency vs Interest Correlation by Domain", x = "Category Interest", y = "Fluency Estimate", color = "Domain") + theme_minimal()
ggsave("fluency_interest_by_domain_correlation_plot.png", width = 8, height = 6)
```

Interest domain split and phonological/semantic similarity + frequency

```{r}
interest_data <- read_csv("../Data/cleaned_data/fluency_interest_estimate.csv")

interest_rating <- interest_data %>%
  dplyr::filter(typeoftrial == "VFT_category_interest") %>%
  select(subject, domain, interest_value = response)

#interest_rating %>%
#  group_by(domain) %>%
#  summarise(median = median(interest_value), mean = mean(interest_value))

interest_groups <- interest_rating %>%
  group_by(domain) %>%
  mutate(
    median_interest = median(interest_value, na.rm = TRUE),
    interest_group = if_else(interest_value >= median_interest, "high_interest", "low_interest")
  ) %>%
  ungroup() %>%
  select(subject, domain, interest_value, interest_group)
  
lexical_domain_interest_groups <- all_lexical_results %>%
  left_join(interest_groups, by = c("Subject" = "subject", "domain" = "domain")) %>%
  dplyr::filter(!is.na(interest_group))

lexical_domain_interest_summary <- lexical_domain_interest_groups %>%
  group_by(domain, interest_group) %>%
  summarise(
    mean_semantic_similarity = mean(Semantic_Similarity, na.rm = TRUE),
    mean_phonological_similarity = mean(Phonological_Similarity, na.rm = TRUE),
    mean_frequency = mean(Frequency_Value, na.rm = TRUE),
    .groups = "drop"
  )

subject_summary <- lexical_domain_interest_groups %>%
  group_by(Subject, domain, interest_group) %>%
  summarise(
    semantic_similarity = mean(Semantic_Similarity, na.rm = TRUE),
    phonological_similarity = mean(Phonological_Similarity, na.rm = TRUE),
    frequency = mean(Frequency_Value, na.rm = TRUE),
    .groups = "drop"
  )

subject_level_interest_summary <- subject_summary %>%
  group_by(domain, interest_group) %>%
  summarize(
    mean_semantic_similarity = mean(semantic_similarity, na.rm = TRUE),
    mean_phonological_similarity = mean(phonological_similarity, na.rm = TRUE),
    mean_frequency = mean(frequency, na.rm = TRUE),
    .groups = "drop"
  )

print(lexical_domain_interest_summary)
print(subject_level_interest_summary)
```
Plots

```{r}
#Plotting semantic similarity across groups
ggplot(lexical_domain_interest_summary, aes(x = interest_group, y = mean_semantic_similarity, fill = interest_group)) +
  geom_col() +
  facet_wrap(~ domain) +
  labs(title = "Mean Semantic Similarity Across Domain Interest Groups", x = NULL, y = "Mean Semantic Similarity") +
  theme_minimal() +
  theme(legend.title = element_blank())
ggsave("semantic_similarity_across_domain_interest.png", width = 8, height = 5, dpi = 300)


#Plotting phonological similarity across groups
ggplot(lexical_domain_interest_summary, aes(x = interest_group, y = mean_phonological_similarity, fill = interest_group)) +
  geom_col() +
  facet_wrap(~ domain) +
  labs(title = "Mean Phonological Similarity Across Domain Interest Groups", x = NULL, y = "Mean Phonological Similarity") +
  theme_minimal() +
  theme(legend.title = element_blank())
ggsave("phonological_similarity_across_domain_interest.png", width = 8, height = 5, dpi = 300)


#Plotting frequency across groups
ggplot(lexical_domain_interest_summary, aes(x = interest_group, y = mean_frequency, fill = interest_group)) +
  geom_col() +
  facet_wrap(~ domain) +
  labs(title = "Mean Frequency Across Domain Interest Groups", x = NULL, y = "Mean Frequency") +
  theme_minimal() +
  theme(legend.title = element_blank())
ggsave("frequency_across_domain_interest.png", width = 8, height = 5, dpi = 300)

```

Prediction vs Actual Fluency Regression
```{r}
#Reading in fluency data
fluency_data <- read_csv("../Data/cleaned_data/fluency_data.csv")

#Calculating the number of fluency responses per participant per domain
fluency_number = fluency_data %>%
  group_by(Subject, domain) %>%
  summarise(
    fluency_number = n(), 
    .groups = "drop"
  )

#Reading in predicted fluency estimate
fluency_wide <- read.csv("../Data/cleaned_data/fluency_interest_estimate.csv")%>%
  select(-rt)%>%
  pivot_wider(names_from = typeoftrial, values_from = response)
#View(fluency_wide)

#Combining actual and estimated fluency
fluency_regression <- fluency_wide %>%
  left_join(fluency_number, by = c("subject" = "Subject", "domain"))
#View(fluency_regression)

fluency_regression_model <- lm(fluency_number ~ VFT_estimate, data = fluency_regression)
summary(fluency_regression_model)

ggplot(fluency_regression, aes(x = VFT_estimate, y = fluency_number)) +
  geom_point(alpha = 0.4, color = "steelblue") + 
  geom_smooth(method = "lm", color = "darkblue", se = TRUE) +
  labs(title = "Predicted vs Actual Fluency Score",
       x = "Estimated Fluency",
       y = "Actual Fluency Score") +
  theme_minimal()
ggsave("fluency_prediction_regression.png", width = 8, heigh = 6, dpi = 300)

```

Lexical Cues and Fluency Regression 
```{r}
lexical_data_long_form <- all_lexical_results %>%
  group_by(Subject, domain) %>%
  summarise(
    mean_semantic = mean(Semantic_Similarity, na.rm = TRUE),
    mean_phonological = mean(Phonological_Similarity, na.rm = TRUE),
    mean_frequency = mean(Frequency_Value, na.rm = TRUE),
    .groups = "drop"
  ) %>%
  pivot_longer(
    cols = c(mean_semantic, mean_phonological, mean_frequency),
    names_to = "cue",
    values_to = "value"
  ) %>%
  left_join(fluency_number, by = c("Subject", "domain"))

lexical_model <- lexical_data_long_form %>%
  group_by(cue) %>%
  nest() %>%
  mutate(
    model = map(data, ~ lmer(fluency_number ~ value + domain + (1|Subject), 
                            data = .x)),
    summary = map(model, summary)
  )

lexical_model %>%
  mutate(walk(summary, print))

ggplot(lexical_data_long_form, aes(x = value, y = fluency_number)) + 
  geom_point(alpha = 0.3, color = "steelblue") +
  geom_smooth(method = "lm", color = "darkblue", se = TRUE) +
  facet_wrap(~ cue, scales = "free_x",
             labeller = labeller(cue = c(
               mean_semantic = "Semantic Similarity",
               mean_phonological = "Phonological Similarity",
               mean_frequency = "Frequency"
             ))) +
  labs(title = "Lexical Cues vs Fluency Score",
       x = "Cue Value",
       y = "Fluency Score") +
  theme_minimal()
ggsave("lexical_cues_fluency_regression.png", width = 12, height = 5, dpi = 300)
```

```{r, fig.width = 12, fig.height = 8}
lexical_model <- lexical_data_long_form %>%
  group_by(cue) %>%
  nest() %>%
  mutate(
    model = map(data, ~ lmer(fluency_number ~ value * domain + (1|Subject), 
                            data = .x)),
    summary = map(model, summary)
  )

lexical_model %>%
  mutate(walk(summary, print))

ggplot(lexical_data_long_form, aes(x = value, y = fluency_number)) + 
  geom_point(alpha = 0.3, color = "steelblue") +
  geom_smooth(method = "lm", color = "darkblue", se = TRUE) +
  facet_wrap(cue ~ domain, scales = "free_x",
             labeller = labeller(cue = c(
               mean_semantic = "Semantic Similarity",
               mean_phonological = "Phonological Similarity",
               mean_frequency = "Frequency"
             ))) +
  labs(title = "Lexical Cues vs Fluency Score",
       x = "Cue Value",
       y = "Fluency Score") +
  theme_minimal()

tidy(lexical_model$model[[1]])
 
  
```
