---
title: "Reddit_Analysis"
author: "Kyra Brown"
date: "2026-06-05"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r}
library(tidyverse)
library(dplyr)
library(ggplot2)
```

First, grouping demographics data of participants by calculating a short and long form score for each, finding the general median, then splitting participants based on that median.

```{r}
demographics <- read.csv("YOUR_DEMOGRAPHICS_DRIVE_LINK")
demographics <- demographics %>% mutate (
  long_form_score = long_NewsArticles + long_FictionBooks + long_NonFictionBooks + long_EssaysBlogsNewsletters + long_Podcasts,
  short_form_score = social_Twitter + social_Facebook + social_TikTok + social_Reddit + social_YouTube + social_Instagram + social_Snapchat
)

median_long_form <- median(demographics$long_form_score, na.rm = TRUE) #9
median_short_form <- median(demographics$short_form_score, na.rm = TRUE) #11

demographics <- demographics %>% mutate (
  language_exposure_group = case_when(
    long_form_score < median_long_form & short_form_score < median_short_form ~ "low_long_low_short",
    long_form_score < median_long_form & short_form_score >= median_short_form ~ "low_long_high_short",
    long_form_score >= median_long_form & short_form_score < median_short_form ~ "high_long_low_short",
    long_form_score >= median_long_form & short_form_score >= median_short_form ~ "high_long_high_short",
  )
  )
```

Next, forming clusters for subreddits (entertainment, advice, academic, learning, geographic, creative, news, athletic, career, cosmetic, general, food, music, religion (NA, for any which didn't fit these categories))

```{r}
subreddit_data <- read_csv("~/Library/CloudStorage/OneDrive-BowdoinCollege/Desktop/fluency-individual-variance/Data/subreddit_data (1).csv")
subreddit_counts <- subreddit_data %>% 
  count(corrected_subreddit, sort = TRUE)
View(subreddit_counts)

top_150_subs <- subreddit_data %>% 
  count(corrected_subreddit, sort = TRUE) %>%
  head(150)

#subreddit categories manually coded, see "top_150_subs_categorized.csv."

category_map <- read_csv("top_150_subs_categorized.csv")
subreddit_data_categorized <- subreddit_data %>% left_join(category_map, by = "corrected_subreddit")
view(subreddit_data_categorized)
subreddit_data_categorized %>% count(category, sort = TRUE)

subreddit_data_categorized <- subreddit_data %>% left_join(category_map, by = "corrected_subreddit") %>% left_join(category_map, by = c("alt_subreddit_1" = "corrected_subreddit"), suffix = c("", "_alt")) %>% dplyr::mutate(category = coalesce(category, category_alt)) %>% dplyr::select(-category_alt)
subreddit_data_categorized %>% count(category, sort = TRUE)
```

Finally, fluency and interest correlations calculated and range box plots (interest and fluency spread) formed

```{r}
fluency_wide <- read.csv("~/Library/CloudStorage/OneDrive-BowdoinCollege/Desktop/fluency-individual-variance/Data/fluency_interest_estimate.csv")%>%
  select(-rt)%>%
  pivot_wider(names_from = typeoftrial, values_from = response)
View(fluency_wide)

ggplot(fluency_wide, aes(x = domain, y = VFT_category_interest)) + geom_boxplot() + labs(title = "Interest Spread by Domain")
ggsave("interest_spread_by_domain_plot.png", width = 8, height = 6)

ggplot(fluency_wide, aes(x = domain, y = VFT_estimate)) + geom_boxplot() + labs(title = "Fluency Spead by Domain")
ggsave("fluency_spread_by_domain_plot.png", width = 8, height = 6)

fluency_wide %>% group_by(domain) %>% summarize(correlation = cor(VFT_category_interest, VFT_estimate, use = "complete.obs"))
```