---
title: "Reddit_Analysis"
author: "Kyra Brown"
date: "2026-06-05"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r}
library(tidyverse)
library(dplyr)
library(ggplot2)
library(readr)
library(Rtsne)
library(ggrepel)
library(tidyr)
library(stringr)
```

1) Grouping demographics data of participants into high short/long, low short/long, high short low long, and low short high long and comparing across lexical data.

```{r}
demographics <- read.csv("../Data/cleaned_data/demographics_data.csv")
demographics <- demographics %>% mutate (
  long_form_score = long_NewsArticles + long_FictionBooks + long_NonFictionBooks + long_EssaysBlogsNewsletters + long_Podcasts,
  short_form_score = social_Twitter + social_Facebook + social_TikTok + social_Reddit + social_YouTube + social_Instagram + social_Snapchat
)

median_long_form <- median(demographics$long_form_score, na.rm = TRUE) #9
median_short_form <- median(demographics$short_form_score, na.rm = TRUE) #11

demographics <- demographics %>% mutate (
  language_exposure_group = case_when(
    long_form_score < median_long_form & short_form_score < median_short_form ~ "low_long_low_short",
    long_form_score < median_long_form & short_form_score >= median_short_form ~ "low_long_high_short",
    long_form_score >= median_long_form & short_form_score < median_short_form ~ "high_long_low_short",
    long_form_score >= median_long_form & short_form_score >= median_short_form ~ "high_long_high_short",
  )
  )

demographics %>% 
  count(language_exposure_group)

#animals lexical results
all_lexical_results <- bind_rows(read_csv("~/Library/CloudStorage/OneDrive-BowdoinCollege/Documents/GitHub/fluency-individual-variance/Analysis/forager/output/animals_forager_results/lexical_results.csv") %>%
                                   mutate(domain = "animals", Subject = as.character(Subject)),
                                 read_csv("~/Library/CloudStorage/OneDrive-BowdoinCollege/Documents/GitHub/fluency-individual-variance/Analysis/forager/output/authors_forager_results/lexical_results.csv") %>%
                                   mutate(domain = "authors", Subject = as.character(Subject)),
                                 read_csv("~/Library/CloudStorage/OneDrive-BowdoinCollege/Documents/GitHub/fluency-individual-variance/Analysis/forager/output/college_majors_forager_results/lexical_results.csv") %>%
                                   mutate(domain = "college_majors", Subject = as.character(Subject)),
                                 read_csv("~/Library/CloudStorage/OneDrive-BowdoinCollege/Documents/GitHub/fluency-individual-variance/Analysis/forager/output/musicians_forager_results/lexical_results.csv") %>%
                                   mutate(domain = "musicians", Subject = as.character(Subject)),
                                 read_csv("~/Library/CloudStorage/OneDrive-BowdoinCollege/Documents/GitHub/fluency-individual-variance/Analysis/forager/output/sportspersons_forager_results/lexical_results.csv") %>%
                                   mutate(domain = "sportspersons", Subject = as.character(Subject)),
                                 )
  
lexical_language_exposure_groups <- all_lexical_results %>%
  left_join(demographics %>% select(subject, language_exposure_group), by = c("Subject" = "subject"))

lexical_language_exposure_groups <- lexical_language_exposure_groups %>% filter(!is.na(language_exposure_group))

lexical_summary <- lexical_language_exposure_groups %>% 
  group_by(domain, language_exposure_group) %>%
  summarise(mean_semantic = mean(Semantic_Similarity, na.rm = TRUE),
            mean_phonological = mean(Phonological_Similarity, na.rm = TRUE),
            mean_frequency = mean(Frequency_Value, na.rm = TRUE),
            .groups = "drop")
print(lexical_summary)
```

```{r}
#Plotting semantic similarity across groups
ggplot(lexical_summary, aes(x = language_exposure_group, y = mean_semantic, fill = language_exposure_group)) +
  geom_col() +
  facet_wrap(~ domain) +
  labs(title = "Mean Semantic Similarity Across Language Exposure Groups", x = NULL, y = "Mean Semantic Similarity") +
  theme_minimal() +
  theme(axis.text.x = element_blank(), legend.title = element_blank())
ggsave("semantic_similarity_across_language_exposure.png", width = 8, height = 5, dpi = 300)


#Plotting phonological similarity across groups
ggplot(lexical_summary, aes(x = language_exposure_group, y = mean_phonological, fill = language_exposure_group)) +
  geom_col() +
  facet_wrap(~ domain) +
  labs(title = "Mean Phonological Similarity Across Language Exposure Groups", x = NULL, y = "Mean Phonological Similarity") +
  theme_minimal() +
  theme(axis.text.x = element_blank(), legend.title = element_blank())
ggsave("phonological_similarity_across_language_exposure.png", width = 8, height = 5, dpi = 300)


#Plotting frequency across groups
ggplot(lexical_summary, aes(x = language_exposure_group, y = mean_frequency, fill = language_exposure_group)) +
  geom_col() +
  facet_wrap(~ domain) +
  labs(title = "Mean Frequency Across Language Exposure Groups", x = NULL, y = "Mean Frequency") +
  theme_minimal() +
  theme(axis.text.x = element_blank(), legend.title = element_blank())
ggsave("frequency_across_language_exposure.png", width = 8, height = 5, dpi = 300)

```

2) Forming clusters for subreddits (entertainment, advice, academic, learning, geographic, creative, news, athletic, career, cosmetic, general, food, music, religion (NA, for any which didn't fit these categories))

```{r}
subreddit_data <- read_csv("../Data/cleaned_data/subreddit_data.csv")
subreddit_counts <- subreddit_data %>% 
  count(corrected_subreddit, sort = TRUE)
View(subreddit_counts)

top_150_subs <- subreddit_data %>% 
  count(corrected_subreddit, sort = TRUE) %>%
  head(150)

#subreddit categories manually coded, see "top_150_subs_categorized.csv."

category_map <- read_csv("top_150_subs_categorized.csv")
subreddit_data_categorized <- subreddit_data %>% left_join(category_map, by = "corrected_subreddit")
view(subreddit_data_categorized)

subreddit_data_categorized <- subreddit_data %>% left_join(category_map, by = "corrected_subreddit") %>% left_join(category_map, by = c("alt_subreddit_1" = "corrected_subreddit"), suffix = c("", "_alt")) %>% dplyr::mutate(category = coalesce(category, category_alt)) %>% dplyr::select(-category_alt)
subreddit_data_categorized %>% count(category, sort = TRUE)
```

Categorizing Subreddit preferences by participant's first input

```{r}
subreddit_data <- read_csv("../Data/cleaned_data/subreddit_data.csv")
subreddit_counts <- subreddit_data %>% 
  count(corrected_subreddit, sort = TRUE)
View(subreddit_counts)

top_150_subs <- subreddit_data %>% 
  count(corrected_subreddit, sort = TRUE) %>%
  head(150)

category_map <- read_csv("../Analysis/top_150_subs_categorized.csv")

manually_added_categories <- tribble(
  ~corrected_subreddit, ~category,
  "r/BPD", "advice",
  "r/Baking", "food",
  "r/Barca", "athletic",
  "r/BostonBruins", "athletic",
  "r/Breath_of_the_Wild", "entertainment",
  "r/Biohackers", "learning",
  "r/BostonBruins", "athletic",
  "r/Buddhism", "religion",
  "r/CFB", "athletic",
  "r/Catholicism", "religion",
  "r/ChatGPT", "learning",
  "r/Costco", "food",
  "r/CozyPlaces", "entertainment",
  "r/CrumblCookies", "food",
  "r/Dreams", "advice",
  "r/EDC", "advice",
  "r/EDH", "entertainment",
  "r/EngagementRings", "creative",
  "r/FigureSkating", "athletic",
  "r/FinancialCareers", "academic and career",
  "r/Forex", "academic and career",
  "r/FundieSnarkUncensored", "religion",
  "r/GaySoundsShitposts", "entertainment",
  "r/GaylorSwift", "entertainment",
  "r/Hair", "creative",
  "r/Handwriting", "creative",
  "r/HomeworkHelp", "academic and career",
  "r/HonkaiStarRail", "entertainment",
  "r/IdiotsInCars", "entertainment",
  "r/Indianapolis", "geographic",
  "r/Jujutsufolk", "entertainment",
  "r/MCFC", "athletic",
  "r/Millennials", "advice",
  "r/Mommit", "advice",
  "r/MurderedByWords", "entertainment",
  "r/NoSleep", "entertainment",
  "r/NonCredibleDefense", "geographic", 
  "r/Omaha", "geographic",
  "r/OnePiece", "entertainment",
  "r/Reverse1999", "entertainment",
  "r/RoastMe", "advice", 
  "r/StockMarket", "learning",
  "r/UXDesign", "academic and career",
  "r/math", "academic and career",
  "r/clinicalresearch", "academic and career",
  "r/celestegame", "entertainment",
  "r/surfing", "athletic",
  "r/TraderJoes", "food",
  "r/asexuality", "advice",
  "r/apples", "food",
  "r/ftm", "advice",
  "r/uswnt", "athletic",
  "r/sentinelsmultiverse", "entertainment",
  "r/deloitte", "academic and career",
  "r/peloton", "athletic",
  "r/philosophy", "learning",
  "r/vegan", "food",
  "r/rance", "geographic",
  "r/simpleliving", "learning",
  "r/tea", "food",
  "r/whatisthisbird", "learning",
  "r/vexillology", "learning",	
  "r/trees", "food",
  "r/foodiesnark", "food"			
 )

category_map_complete <- bind_rows(category_map, manually_added_categories)
  

subreddit_data_categorized <- subreddit_data %>%
  left_join(category_map_complete, by = "corrected_subreddit") %>%
  left_join(category_map_complete, by = c("alt_subreddit_1" = "corrected_subreddit"), suffix = c("", "_alt1")) %>%
  left_join(category_map_complete, by = c("alt_subreddit_2" = "corrected_subreddit"), suffix = c("", "_alt2")) %>%
  mutate(category = coalesce(category, category_alt1, category_alt2)) %>%
  select(-category_alt1, -category_alt2)

view(subreddit_data_categorized)
subreddit_data_categorized %>% count(category, sort = TRUE)

subreddit_data_categorized <- subreddit_data_categorized %>%
  mutate(category = replace_na(category, "other"))

primary_buckets <- subreddit_data_categorized %>%
  filter(tag == 1) %>%
  transmute(Subject, primary_subreddit = corrected_subreddit, primary_bucket = category)

df_analysis <- subreddit_data_categorized %>%
  left_join(primary_buckets, by = "Subject") %>%
  mutate(matches_primary = (category == primary_bucket))

other_subreddit_alignment_check <- df_analysis %>%
  group_by(Subject, primary_subreddit, primary_bucket) %>%
  summarise(
    total_subreddits = n(),
    matching_category = sum(matches_primary, na.rm = TRUE),
    unknown_category = sum(is.na(category)),
    percentage_match = round(100 * matching_category / total_subreddits, 1),
    mismatched_subreddits = paste(corrected_subreddit[!matches_primary & !is.na(category)], collapse = ", "), .groups = "drop"
  ) %>%
  arrange(desc(percentage_match))

print(other_subreddit_alignment_check, n = Inf)

category_distribution <- df_analysis %>%
  count(category, sort = TRUE) %>%
  mutate(pct = round(100 * n / sum(n), 1))

print(category_distribution)

subreddit_data_categorized %>%
  filter(is.na(category))%>%
  count(corrected_subreddit, sort = TRUE)

other_subreddit_alignment_check %>%
  filter(primary_bucket == "other") %>%
  select(Subject, primary_subreddit)

primary_bucket_summary <- primary_buckets %>%
  count(primary_bucket, sort = TRUE) %>%
  mutate(pct = round(100 * n / sum(n), 1))
print(primary_bucket_summary)

participant_consistency_summary <- other_subreddit_alignment_check %>%
  group_by(primary_bucket) %>%
  summarise(
    n_participants = n(),
    average_pct_match = round(mean(percentage_match, na.rm = TRUE), 1),
    median_pct_match = round(median(percentage_match, na.rm = TRUE), 1)) %>%
  arrange(desc(n_participants))
print(participant_consistency_summary)

other_subreddit_alignment_check %>%
  filter(primary_bucket == "religion")

primary_buckets %>%
  filter(primary_bucket == "religion")

  
```

Plots of subreddits listed, first subreddit stats, and subreddit category consistency

```{r}
#distribution of subreddits listed per participant
subreddit_count_per_participant <- subreddit_data_categorized %>%
  group_by(Subject) %>%
  summarise(n_subreddits = n())

ggplot(subreddit_count_per_participant, aes(x = n_subreddits)) + 
  geom_bar(fill = "steelblue") +
  scale_x_continuous(breaks = seq(0, 30, 5)) +
  labs(
    title = "Distribution of Subreddit Count Per Participant",
    x = "Number of Subreddits Listed",
    y = "Number of Participants") + theme_minimal()
ggsave("subreddit_count_distribution.png", width = 8, height = 5, dpi = 300)


#distribution of primary buckets people's first subreddit input fell into
ggplot(primary_bucket_summary, aes(x = reorder(primary_bucket, pct), y = pct)) +
  geom_col(fill = "steelblue") +
  coord_flip() +
  scale_y_continuous(breaks = seq(0, 30, 5)) +
  labs(
    title = "First Subreddit Category Distribution",
    x = "Category",
    y = "Percentage of Participants (%)"
  ) + theme_minimal()
ggsave("primary_bucket_distribution.png", width = 8, height = 5, dpi = 300)

#Participant consistency based on primary bucket
ggplot(participant_consistency_summary, aes(x = n_participants, y = average_pct_match, size = n_participants, label = primary_bucket)) +
  geom_point(alpha = 0.6, color = "steelblue") +
  geom_text(vjust = -1, size = 3) +
  scale_size_continuous(range = c(3, 12)) + 
  scale_x_continuous(breaks = seq(0, 30, 5)) +
  scale_y_continuous(breaks = seq(0, 60, 5)) +
  labs(
    title = "Category Consistency vs. Popularity",
    x = "Number of Participants",
    y = "Average % of Subreddits in Same Category as Primary",
    size = "N Participants",
  ) +
  theme_minimal() + theme(legend.position = "none")
ggsave("category_consistency_and_popularity.png", width = 8, height = 6, dpi = 300)

```

Exploring subreddits named over time

```{r}
reddit_raw_data <- read_csv("../Data/raw_data/reddit_data.csv")

subreddit_reaction_time <- reddit_raw_data %>%
  filter(task == "VFT", domain == "subreddits") %>%
  select(subject, response_times) %>%
  
mutate(response_times = str_remove_all(response_times, "\\[|\\]")) %>%
  separate_rows(response_times, sep = ",") %>%
  mutate(response_times = as.numeric(str_trim(response_times))) %>%
  group_by(subject) %>%
  mutate(
    subreddit_number = row_number(),
    cumulative_rt_s = cumsum(response_times) / 1000
  ) %>%
  ungroup()

max_time <- ceiling(max(subreddit_reaction_time$cumulative_rt_s, na.rm = TRUE))

subjects <- unique(subreddit_reaction_time$subject)

cumulative_curve <- tibble(second = 1:max_time) %>%
  mutate(
    avg_subreddits = sapply(second, function(s) {
      mean(sapply(subjects, function(subj) {
        sum(subreddit_reaction_time$cumulative_rt_s[subreddit_reaction_time$subject == subj] <= s, na.rm = TRUE)
      }))
    })
  )

print(cumulative_curve, n = 90)

ggplot(cumulative_curve, aes(x = second, y = avg_subreddits)) +
  geom_col(color = "steelblue") + 
  scale_x_continuous(breaks = seq(0, max_time, 10)) +
  scale_y_continuous(breaks = seq(0, ceiling(max(cumulative_curve$avg_subreddits)), 1)) +
  labs(
    title = "Average Subreddits Named Over Time",
    x = "Cumulative Time (seconds)",
    y = "Average Number of Subreddits Named"
  ) + theme_minimal()

ggsave("average_subreddits_named_over_time.png", width = 8, height = 6, dpi = 300)

```

 subreddits named over time (in 30 second intervals)
 
```{r}
reddit_raw_data <- read_csv("../Data/raw_data/reddit_data.csv")

subreddit_reaction_time <- reddit_raw_data %>%
  filter(task == "VFT", domain == "subreddits") %>%
  select(subject, response_times) %>%
  
mutate(response_times = str_remove_all(response_times, "\\[|\\]")) %>%
  separate_rows(response_times, sep = ",") %>%
  mutate(response_times = as.numeric(str_trim(response_times))) %>%
  group_by(subject) %>%
  mutate(
    subreddit_number = row_number(),
    cumulative_rt_s = cumsum(response_times) / 1000
  ) %>%
  ungroup()

max_time <- ceiling(max(subreddit_reaction_time$cumulative_rt_s, na.rm = TRUE))

subjects <- unique(subreddit_reaction_time$subject)

number_of_subjects <- length(subjects)

percentage_cumulative_curve <- tibble(second = 1:max_time) %>%
  mutate(
    avg_subreddits = sapply(second, function(s) {
      mean(sapply(subjects, function(subj) {
        sum(subreddit_reaction_time$cumulative_rt_s[subreddit_reaction_time$subject == subj] <= s, na.rm = TRUE)
      }))
    }),
    percent_named_one_subreddit = sapply(second, function(s) {
      100 * mean(sapply(subjects, function(subj) {
        any(subreddit_reaction_time$cumulative_rt_s[subreddit_reaction_time$subject == subj] <= s, na.rm = TRUE)
      }))
    })
  )


cumulative_curve <- tibble(second = 1:max_time) %>%
  mutate(
    avg_subreddits = sapply(second, function(s) {
      mean(sapply(subjects, function(subj) {
        sum(subreddit_reaction_time$cumulative_rt_s[subreddit_reaction_time$subject == subj] <= s, na.rm = TRUE)
      }))
    })
  )

print(cumulative_curve, n = 90)

ggplot(cumulative_curve, aes(x = second, y = avg_subreddits)) +
  geom_col(color = "steelblue") + 
  scale_x_continuous(breaks = seq(0, max_time, 30)) +
  scale_y_continuous(breaks = seq(0, ceiling(max(cumulative_curve$avg_subreddits)), 1)) +
  labs(
    title = "Average Subreddits Named Over Time (30 sec interval)",
    x = "Cumulative Time (seconds)",
    y = "Average Number of Subreddits Named"
  ) + theme_minimal()

ggsave("average_subreddits_named_over_time_30sec_interval.png", width = 8, height = 6, dpi = 300)

ggplot(percentage_cumulative_curve, aes(x = second, y = percent_named_one_subreddit)) +
  geom_line(color = "steelblue", linewidth = 1) + 
  coord_cartesian(xlim = c(0,30)) +
  scale_x_continuous(breaks = seq(0, 30, 5)) +
  scale_y_continuous(breaks = seq(0,100, 10), limits = c(0, 100)) +
  labs(
    title = "Percentage of Participants who Named one Subreddit",
    x = "Cumulative Time (seconds)",
    y = "% of Participants"
  ) + theme_minimal()

ggsave("percentage_participants_who_named_subreddit_over_time.png", width = 8, height = 6, dpi = 300)


```


3) Fluency and interest correlations calculated and range box plots (interest and fluency spread) formed

```{r}
fluency_wide <- read.csv("../Data/cleaned_data/fluency_interest_estimate.csv")%>%
  select(-rt)%>%
  pivot_wider(names_from = typeoftrial, values_from = response)
View(fluency_wide)

#Box plot of interest spread across domains
ggplot(fluency_wide, aes(x = domain, y = VFT_category_interest)) + geom_boxplot() + labs(title = "Interest Spread by Domain")
ggsave("interest_spread_by_domain_plot.png", width = 8, height = 6)

#Box plot of fluency spread across domains
ggplot(fluency_wide, aes(x = domain, y = VFT_estimate)) + geom_boxplot() + labs(title = "Fluency Spead by Domain")
ggsave("fluency_spread_by_domain_plot.png", width = 8, height = 6)

#Summary of correlation between fluency and interest per domain
fluency_wide %>% group_by(domain) %>% summarize(correlation = cor(VFT_category_interest, VFT_estimate, use = "complete.obs"))

#Plot of correlation, annotated ^
correlation_labels <- fluency_wide %>%
  group_by(domain) %>%
  summarize(correlation = round(cor(VFT_category_interest, VFT_estimate, use = "complete.obs"), 2), x = 85, y = max(VFT_estimate, na.rm = TRUE) * 0.9)
correlation_labels$y <- c(55, 50, 45, 40, 35)

ggplot(fluency_wide, aes(x = VFT_category_interest, y = VFT_estimate, color = domain)) + geom_point(alpha = 0.4) + geom_smooth(method = "lm", se = FALSE) + geom_text(
  data = correlation_labels, aes(x = x, y = y, label = paste0("r" = correlation), color = domain), show.legend = FALSE, size = 3.5) +
  labs(title = "Fluency vs Interest Correlation by Domain", x = "Category Interest", y = "Fluency Estimate", color = "Domain") + theme_minimal()
ggsave("fluency_interest_by_domain_correlation_plot.png", width = 8, height = 6)
```

Interest domain split and phonological/semantic similarity + frequency

```{r}
interest_data <- read_csv("../Data/cleaned_data/fluency_interest_estimate.csv")

interest_rating <- interest_data %>%
  dplyr::filter(typeoftrial == "VFT_category_interest") %>%
  select(subject, domain, interest_value = response)

#interest_rating %>%
#  group_by(domain) %>%
#  summarise(median = median(interest_value), mean = mean(interest_value))

interest_groups <- interest_rating %>%
  group_by(domain) %>%
  mutate(
    median_interest = median(interest_value, na.rm = TRUE),
    interest_group = if_else(interest_value >= median_interest, "high_interest", "low_interest")
  ) %>%
  ungroup() %>%
  select(subject, domain, interest_value, interest_group)
  
lexical_domain_interest_groups <- all_lexical_results %>%
  left_join(interest_groups, by = c("Subject" = "subject", "domain" = "domain")) %>%
  dplyr::filter(!is.na(interest_group))

lexical_domain_interest_summary <- lexical_domain_interest_groups %>%
  group_by(domain, interest_group) %>%
  summarise(
    mean_semantic_similarity = mean(Semantic_Similarity, na.rm = TRUE),
    mean_phonological_similarity = mean(Phonological_Similarity, na.rm = TRUE),
    mean_frequency = mean(Frequency_Value, na.rm = TRUE),
    .groups = "drop"
  )

subject_summary <- lexical_domain_interest_groups %>%
  group_by(Subject, domain, interest_group) %>%
  summarise(
    semantic_similarity = mean(Semantic_Similarity, na.rm = TRUE),
    phonological_similarity = mean(Phonological_Similarity, na.rm = TRUE),
    frequency = mean(Frequency_Value, na.rm = TRUE),
    .groups = "drop"
  )

subject_level_interest_summary <- subject_summary %>%
  group_by(domain, interest_group) %>%
  summarize(
    mean_semantic_similarity = mean(semantic_similarity, na.rm = TRUE),
    mean_phonological_similarity = mean(phonological_similarity, na.rm = TRUE),
    mean_frequency = mean(frequency, na.rm = TRUE),
    .groups = "drop"
  )

print(lexical_domain_interest_summary)
print(subject_level_interest_summary)
```
Plots

```{r}
#Plotting semantic similarity across groups
ggplot(lexical_domain_interest_summary, aes(x = interest_group, y = mean_semantic_similarity, fill = interest_group)) +
  geom_col() +
  facet_wrap(~ domain) +
  labs(title = "Mean Semantic Similarity Across Domain Interest Groups", x = NULL, y = "Mean Semantic Similarity") +
  theme_minimal() +
  theme(legend.title = element_blank())
ggsave("semantic_similarity_across_domain_interest.png", width = 8, height = 5, dpi = 300)


#Plotting phonological similarity across groups
ggplot(lexical_domain_interest_summary, aes(x = interest_group, y = mean_phonological_similarity, fill = interest_group)) +
  geom_col() +
  facet_wrap(~ domain) +
  labs(title = "Mean Phonological Similarity Across Domain Interest Groups", x = NULL, y = "Mean Phonological Similarity") +
  theme_minimal() +
  theme(legend.title = element_blank())
ggsave("phonological_similarity_across_domain_interest.png", width = 8, height = 5, dpi = 300)


#Plotting frequency across groups
ggplot(lexical_domain_interest_summary, aes(x = interest_group, y = mean_frequency, fill = interest_group)) +
  geom_col() +
  facet_wrap(~ domain) +
  labs(title = "Mean Frequency Across Domain Interest Groups", x = NULL, y = "Mean Frequency") +
  theme_minimal() +
  theme(legend.title = element_blank())
ggsave("frequency_across_domain_interest.png", width = 8, height = 5, dpi = 300)

```

4) t-SNE of interest data

```{r}
emb <- read_csv("../Analysis/forager/data/lexical_data/interests/USE_embeddings.csv")

X <- t(as.matrix(emb))
labels <- colnames(emb)
dim(X)
head(labels)

dim(emb)
dim(tsne_out$Y)
ncol(emb)
nrow(emb)

set.seed(123)
tsne_out <- Rtsne(X, perplexity = 15, check_duplicates = FALSE, pca = TRUE)
tsne_df <- data.frame(interest = labels, x = tsne_out$Y[,1], y = tsne_out$Y[,2])

ggplot(tsne_df, aes(x, y, label = interest)) + geom_point(size = 2) + geom_text_repel(size = 3) + theme_minimal()

```

5) Preparation for Forager (semantic embeddings, cues, frequencies)
```{r}
#Unique vocab lists

#Authors
unique_author_enteries <- read.csv("../Data/cleaned_data/fluency_data.csv") %>%
  filter(domain == "authors") %>% distinct(corrected_response)
View(unique_author_enteries)
write.csv(unique_author_enteries, "Analysis/forager/data/lexical_data/authors/vocab.csv", row.names = FALSE)

#Musicians
unique_musician_enteries <- read.csv("../Data/cleaned_data/fluency_data.csv") %>%
  filter(domain == "musicians") %>% distinct(corrected_response)
View(unique_musician_enteries)
write.csv(unique_musician_enteries, "Analysis/forager/data/lexical_data/musicians/vocab.csv", row.names = FALSE)

#Sportspersons
unique_sportspersons_enteries <- read.csv("../Data/cleaned_data/fluency_data.csv") %>%
  filter(domain == "sportspersons") %>% distinct(corrected_response)
View(unique_sportspersons_enteries)
write.csv(unique_sportspersons_enteries, "Analysis/forager/data/lexical_data/sportspersons/vocab.csv", row.names = FALSE)

#College Majors
unique_college_majors_enteries <- read.csv("../Data/cleaned_data/fluency_data.csv") %>%
  filter(domain == "college_majors") %>% distinct(corrected_response)
View(unique_college_majors_enteries)
write.csv(unique_college_majors_enteries, "Analysis/forager/data/lexical_data/college majors/vocab.csv", row.names = FALSE)

path <- "Analysis/forager/data/lexical_data/college majors/vocab.csv"
read.csv(path) %>% rename(vocab = corrected_response) %>% write.csv(path, row.names = FALSE)

#Interests
unique_interest_enteries <- read.csv("../Data/cleaned_data/interests_data.csv") %>%
  distinct(corrected_interest) %>% rename(vocab = corrected_interest)
View(unique_interest_enteries)
write.csv(unique_interest_enteries, "Analysis/forager/data/lexical_data/interests/vocab.csv", row.names = FALSE)

```

5) Preparation for Forager (phonological matricies)
```{r}
#Changing column name
base_path <- "../Analysis/forager/Data/lexical_data"

domains <- c("authors", "musicians", "sportspersons", "college majors")

for(domain in domains) {
  path <- file.path(base_path, domain, "vocab.csv")
  df <- read.csv(path, stringsAsFactors = FALSE)
  
  if ("vocab" %in% names(df)) {
    df <- df %>% rename(word = vocab)
  }
  
  #Finding weird entries/duplicates
  cat("\n---", domain, "---\n")
  
  duplicates <- df$word[duplicated(df$word)]
  if (length(duplicates) > 0) cat("Duplicates:", paste(duplicates, collapse = ", "), "\n")
  
  weird_chars <- df$word[grepl("[^a-zA-Z0-9 ., '-]|\\(|\\)", df$word)]
  if (length(weird_chars) > 0) cat("Weird Characters:", paste(weird_chars, collapse = ", "), "\n")
  
  #Cleaning data
  df$word <- stri_trans_general(df$word, "Latin-ASCII")
  df$word <- gsub("\\+", " and ", df$word)
  df$word <- gsub("&", " and ", df$word)
  df$word <- gsub("\\s*\\([^)]*\\)", "", df$word)
  df$word <- gsub("[^a-zA-Z0-9 .,\\'-]", "", df$word)
  df$word <- gsub("\\s+", " ", df$word)
  df$word <- trimws(df$word)

  write.csv(df, path, row.names = FALSE)

  cat("Cleaned:", domain, "\n") 
  
}
```

Extra tests (1): Is there a connection between the variety of subreddit categories a person engaged with and their fluency?

```{r}
subreddit_variety_data <- subreddit_data_categorized %>%
  group_by(Subject) %>%
  summarize(unique_categories = n_distinct(category, na.rm = TRUE)) %>%
  left_join(fluency_wide, by = c("Subject" = "subject"))

ggplot(subreddit_variety_data, aes(x = unique_categories, y = VFT_estimate)) + geom_point() + geom_smooth(method = "lm") + labs(title = "Category Variety vs Fluency")

cor(subreddit_variety_data$unique_categories, subreddit_variety_data$VFT_estimate, use = "complete.obs")

```

Extra tests (2): Do fluency scores differ by language exposure group?

```{r}
exposure_data <- demographics %>%
  left_join(fluency_wide, by = "subject")

ggplot(exposure_data, aes(x = language_exposure_group, y = VFT_estimate)) + geom_boxplot() + theme(axis.text.x = element_text(angle = 45, hjust = 1)) + labs(title = "Fluency by Language Exposure")

#ANOVA testing if fluency differs across exposure, at least one group has a different mean fluency than the others
summary(aov(VFT_estimate ~ language_exposure_group, data = exposure_data))

#Tukey's test, reveling significant difference between low long, high short and other groups in fluency production
TukeyHSD(aov(VFT_estimate ~ language_exposure_group, data = exposure_data))
```

